---
title: "Nevyn Neal - hw_02"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
```{r}
#Correct sub-setting followed by original question:
mtcars[mtcars$cyl < 6,] #mtcars[mtcars$cyl < 6]
mtcars[2:3,] #mtcars[-1:3,]
mtcars[mtcars$cyl == 8, ] #mtcars[mtcars$cyl = 8, ]
mtcars[mtcars$cyl == 4 | mtcars$cyl == 6, ] # mtcars[mtcars$cyl == 4 | 6, ]
```

## Question 2
Since NA is a logical type variable, x[NA] coerces the integers of x to their NA_integer value, NA. 

## Question 3
R subsetting defaults to indexing columns when row or columns are not specified (using commas). Because mtcars does not have 15 columns, the index is out of bounds. 
'mtcars[1:15,]' indexes rows instead of columns, and since there are at least 15 rows in the mtcars dataframe, those are returned successfully.

## Question 4
The first line creates a 3 row matrix with 9 values (implicitly defines 3 columns). Some of the values in the initial matrix are NA. The next line returns the indicies of x in which is.na(x) == true, then replaces the values at those locations with 0.

## Question 5
```{r}
data("mtcars")
mtcars$mpg2 = 'null'
mtcars$mpg2[mtcars$mpg < 16] = 'Low'
mtcars$mpg2[mtcars$mpg >= 16 & mtcars$mpg < 21 ] = 'Low_intermediate'
mtcars$mpg2[mtcars$mpg >= 21 & mtcars$mpg < 26 ] = 'Intermediate_high'
mtcars$mpg2[mtcars$mpg >= 26] = 'Low_intermediate'
```



